A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-28 ICLP Paper/samplepaper.tex
working state to continue from

\paragraph{Multi-shot Solving:}
Multi-shot solving ASP allows solving logic programs dynamically in sequential order. This can be manipulated using APIs implementation via an imperative programming language. Such programming language is used to control the grounding and solving processes and allows the usage of external variables that could be set to $True$ or $False$ to control some logic rules. The main advantage of \emph{multi-shot} solving is to avoid the re-grounding and exploit conflicts learned over time.
%ASP is a paradigm that deals with continuously changing logic programs. In a single-shot approach, an ASP system takes a logic program, computes answer sets and exits. However, the idea of Multi-shot is to consider evolving grounding and solving processes. \emph{clingo} systems enhances the ASP declaritive language with control capacities.

@@

Size & \multicolumn{3}{c}{$50\times15$} & \multicolumn{3}{c}{$50\times20$} & \multicolumn{3}{c}{$100\times20$}\\
Strategy & Makespan & Time & Ints & Makespan & Time & Ints & Makespan & Time & Ints % \\
    \midline% \hline\\[-2.75mm]
    J-EST            & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    J-MTWR            & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]
    M-EST             & $3083.8$  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & $6031.9$ & $1000.0$ & $6.0$\\
    M-MTWR        & \boldmath{$3060.3$}  & $1000.0$   & $3.0$	& $3287.9$      & $986.1$ & $3.9$ & \boldmath{$5948.6$} & $1000.0$ & $7.0$\\ 
    [1.5mm]
    M-EST$^\text{\,dyn}$            & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $4.0$ & $6115.1$ & $1000.0$ & $7.0$% \\[1.5mm]

>>>>

\paragraph{Multi-shot ASP solving} \citep{gekakasc17a}
allows for iterative reasoning processes by controlling and interleaving
the grounding and search phases of a stateful ASP system.
For identifying a collection of rules to instantiate,
the input language of \clingo supports \lstinline{#program name(c).}
directives, where the constant~\lstinline{c} is a placeholder for some value, e.g.,
the current time step in case of a planning problem,
supplied upon instantiating the rules below such a directive.

Multi-shot solving ASP allows solving logic programs dynamically in sequential order. This can be manipulated using APIs implementation via an imperative programming language. Such programming language is used to control the grounding and solving processes and allows the usage of external variables that could be set to $True$ or $False$ to control some logic rules. The main advantage of \emph{multi-shot} solving is to avoid the re-grounding and exploit conflicts learned over time.
%ASP is a paradigm that deals with continuously changing logic programs. In a single-shot approach, an ASP system takes a logic program, computes answer sets and exits. However, the idea of Multi-shot is to consider evolving grounding and solving processes. \emph{clingo} systems enhances the ASP declaritive language with control capacities.

@@

Size & \multicolumn{3}{c}{$50\times15$} & \multicolumn{3}{c}{$50\times20$} & \multicolumn{3}{c}{$100\times20$}\\
Strategy & Makespan & Time & Ints & Makespan & Time & Ints & Makespan & Time & Ints % \\
    \midline% \hline\\[-2.75mm]
    J-EST            & $3524.8$ & $1000.0$   & $2.0$	   & $3540.8$      & $1000.0$ & $2.0$ & $6964.4$ & $1000.0$ & $4.0$\\ 
    J-MTWR            & $3456.2$  & $1000.0$   & $2.0$	& $3561.0$      & $1000.0$ & $2.0$ & $7149.6$ & $1000.0$ & $4.0$\\ 
    [1.5mm]
    M-EST             & $3083.8$  & $1000.0$   & $3.0$	& \boldmath{$3260.3$}      & $944.9$ & $3.5$ & $6031.9$ & $1000.0$ & $6.0$\\
    M-MTWR        & $3060.3$  & $1000.0$   & $3.0$	& $3287.9$      & $986.1$ & $3.9$ & \boldmath{$5948.6$} & $1000.0$ & $7.0$\\ 
    [1.5mm]
    M-EST$^\text{\,d}$            & $3098.4$  & $1000.0$   & $3.0$	& $3309.5$     & $1000.0$ & $4.0$ & $6115.1$ & $1000.0$ & $7.0$ \\
    M-MTWR$^\text{\,d}$            & \boldmath{$3041.6$}  & $1000.0$   & $3.0$	& $3287.0$     & $980.4$ & $3.9$ & $6167.3$ & $1000.0$ & $5.0$
